A Gaussian process model of human electrocorticographic data

### 2019-01-09 paper/main.tex
updated gitignore file, reformatting references
minor citations format update

\documentclass[11pt]{article}
\usepackage[numbers, square, sort, compress]{natbib}
\usepackage{newpxtext,newpxmath}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left]{lineno}
\linenumbers

@@

An increasingly popular approach is to improve the effective spatial
resolution of MEG or scalp EEG data by using a geometric approach
called \textit{beamforming} to solve the biomagnetic or bioelectrical
inverse problem~\cite{Sarv87}.  This approach entails using detailed
brain conductance models (often informed by high spatial resolution
anatomical MRI images) along with the known sensor placements
(localized precisely in 3D space) to reconstruct brain signals
originating from theoretical point sources deep in the brain (and far
from the sensors).  Traditional beamforming approaches must overcome
two obstacles.  First, the inverse problem beamforming seeks to solve
has infinitely many solutions.  Researchers have made traction towards
constraining the solution space by assuming that signal-generating
sources are localized on a regularly spaced grid spanning the brain
and that individual sources are small relative to their distances to
the sensors~\cite{Snyd91, BailEtal01, HillEtal05}.  The second, and in
some ways much more serious, obstacle is that the magnetic fields
produced by external (noise) sources are substantially stronger than
those produced by the neuronal changes being sought (i.e., at deep
structures, as measured by sensors at the scalp).  This means that
obtaining adequate signal quality often requires averaging the
measured responses over tens to hundreds of responses or trials
(e.g., see review by~\cite{HillEtal05}).

@@

\bibliography{CDL-bibliography/memlab.bib}
\bibliographystyle{apa}

>>>>

\documentclass[11pt]{article}
\usepackage[round,sort&compress]{natbib}
\setcitestyle{aysep={}}
\usepackage{newpxtext,newpxmath}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left]{lineno}
\linenumbers

@@

An increasingly popular approach is to improve the effective spatial
resolution of MEG or scalp EEG data by using a geometric approach
called \textit{beamforming} to solve the biomagnetic or bioelectrical
inverse problem~\cite{Sarv87}.  This approach entails using detailed
brain conductance models (often informed by high spatial resolution
anatomical MRI images) along with the known sensor placements
(localized precisely in 3D space) to reconstruct brain signals
originating from theoretical point sources deep in the brain (and far
from the sensors).  Traditional beamforming approaches must overcome
two obstacles.  First, the inverse problem beamforming seeks to solve
has infinitely many solutions.  Researchers have made traction towards
constraining the solution space by assuming that signal-generating
sources are localized on a regularly spaced grid spanning the brain
and that individual sources are small relative to their distances to
the sensors~\cite{Snyd91, BailEtal01, HillEtal05}.  The second, and in
some ways much more serious, obstacle is that the magnetic fields
produced by external (noise) sources are substantially stronger than
those produced by the neuronal changes being sought (i.e., at deep
structures, as measured by sensors at the scalp).  This means that
obtaining adequate signal quality often requires averaging the
measured responses over tens to hundreds of responses or trials~\citep[e.g., see review by][]{HillEtal05}).

@@

\bibliography{memlab}
\bibliographystyle{CSE}
